Untitled

### 2018-08-12 PaperCode.Rmd
Simplify Bootstrapping
I refactored the code for bootstrapping and sampling. This made it easier to understand and allowed me to have a single strapping function that can be modified for high or low memory usage.
I also fine tuned the quantiles

---
title: "Untitled"
author: "Jonathan Bourne"
date: "9 August 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up 2/Figures" #file.path(basewd, "Figures")
TexTables <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up 2/Tables"
source(file.path(CommonCode, "AuxdataLoad.R"))
```

@@

This chunk processes all the areas and combines into a single dataframe
It also cleans all postcodes that are in other LADs out... should it just combine them into the other LADs LSOA?
```{r}
#creates a data frame called DATAdf
source(file.path(SubCode, "LOADandProcessLADData.R"))

@@

@@

Needed for creating the skew plots
```{r}

setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapQuartiles")
BootstrapAllData(DATAdf, LimitValue = 1.3e5, Reps = 501)
BootStrapRes <- LoadBootstrapData()

@@

##MSOA Bootstrap
Used for most of the analysis
```{r}

setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA2")
BootstrapAllData(DATAdf, LimitValue = 1.3e5, Reps = 501, GroupingVars = "MSOA11CD")

#Temporay untill the proper one is complete
setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA2")
BootStrapRes <- LoadBootstrapData()

@@

##This will need to be re-worked when the quartiles are put in and the data is re bootstrapped

```{r}
CleanForPlotClassDiff <- function(df){ #not a seperate function for ease of editing
  df %>% 
  group_by(ID, class) %>%
  summarise(Homes = sum(Homes), LowUse = sum(LowUse)) %>%
  group_by(ID)%>%
  mutate(RatioExvsAct = LowUse/sum(LowUse)) %>%
  mutate(RatioExvsAct = (RatioExvsAct/0.25)-1)
}

#I think I should have 1 plot with high value skew, one plot with low value skew and 1 plot for all data
#These three plots should be shown as a panel of data

CleanForPlotClassDiff(BootStrapRES$ChelseaLON)  %>%
PlotClassDiff(., "Kensington and Chelsea")
SaveFig("ClassdiffChelsea.pdf")

CleanForPlotClassDiff(BootStrapRES$BarrowCUMBRIA) %>% #maybe choose a better place than barrow?
PlotClassDiff(., "Barrow")
SaveFig("ClassdiffBarrow.pdf")

#Plot for all data
All_data_class <- BootStrapRES %>% 
  bind_rows %>%
  select(CountryClass, ID, LowUse, Homes) %>%
  rename(class = CountryClass)%>%
  CleanForPlotClassDiff

All_data_class %>% group_by(class) %>%
  summarise_all(mean)

PlotClassDiff(All_data_class)
SaveFig("ClassdiffAllData.pdf")

@@

CorePstCd <- PstCdLSOA.raw %>%
  left_join(EW2, by = c("lsoa11cd" = "ECODE")) %>%
  select(Postcode,LSOA11CD= lsoa11cd, LAD11CD, LAD11NM, MSOA11CD, Pop)

setwd(file.path(basewd, "VOA data"))

@@

HArtlePool E06000001
COl E02000001
```{r}
LADModelData <-CreateGeogModelData("LAD", "/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA")
LADMean<- MeanModelData(LADModelData, "LAD") %>%
  mutate(AffordRank2 = scale(AffordRank)^2,
         TourismDensityRank = rank(TourismDensity, ties.method = "max"))

  LADMean %>%
  ggplot(aes(x= AffordRank, y = TourismDensityRank, colour = HighVal)) + geom_point()

  LADMean %>%
  ggplot(aes(x= MedianDiffRank, y = LowUseRank, colour = HighVal)) + geom_point()

@@

MSOAModelData <-CreateGeogModelData("MSOA", "/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA") 
MSOAMean <- MeanModelData(MSOAModelData, "MSOA") %>%
  left_join(select(MSOAtoLAD, MSOA11CD, LAD11CD)) %>%
  mutate(AffordRank2 = scale(AffordRank)^2,
         TourismDensityRank = rank(TourismDensity, ties.method = "max"))

 MSOAMean %>%
  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighVal)) + geom_point()

  MSOAMean %>%
  ggplot(aes(x= MedianDiffRank, y = LowUseRank, colour = HighVal)) + geom_point()

  #Great results for the MSOA model predicting High LUP numbers
  ModelFormula <- as.formula(Reference ~ TourismRank+ AffordRank+ AffordRank2)

@@

#Price affordability correlation

Why is there such a large difference between price and affordability at lad level and MSOA level  is this a mistake?
```{r}

cor(LADMean$AffordRatio, LADMean$HomesMedian)
cor(MSOAMean$AffordRatio, MSOAMean$HomesMedian)
```

@@

@@

works well at predicting high numbers of LUPs
 ModelFormula <- as.formula(Reference ~ TourismDensityRank + AffordRank)

@@

set.seed(1983)
TestResample <- 1:100 %>% map(~  resample_partition(LADMean , c(test = 0.2, train = 0.8)))

#Make a lot of models

Combos<-expand.grid(1:2,1:2)

LADModels <- map2_df(.x = c("HighVal", "HighLUP")[Combos[,1]], .y = c(as.formula(Reference ~ HomesMedianRank+ AffordRank), 
                                                         as.formula(Reference ~ TourismDensityRank+ AffordRank))[Combos[,2]],
        ~{
          print(paste(.x,.y))
          LADMean %>% #LADMean %>%
    rename_(Reference = .x ) %>%
  ResampledModelPerf(., TestResample,  .y) %>%
            mutate(Dependent = .x,
                   Formula = toString(.y))

        } ) %>%
  mutate(Formula = ifelse(grepl("Tourism", Formula), "Tourism", "Price"))

MODOut <- 1:length(TestResample) %>% map_df(~{
  Mod2 <- LADMean  %>%
    rename(Reference = HighVal) %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$train)) %>%
  glm(formula = as.formula(Reference ~ TourismDensityRank+ AffordRank), data = ., family=binomial(link='logit'))%>%
    tidy

})

ggplot(MODOut, aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients

LADModels %>%
  group_by(Dependent, Formula) %>%
  summarise(BeatNull = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            meanAcc = mean(Accuracy), #What was the mean accuracy
            NULLMod = mean(AccuracyNull),
            DiffNull = mean(Accuracy-AccuracyNull), #Mean difference relative to NULL
            StatistSignif = t.test(Accuracy,AccuracyNull, alternative = "greater", paired = T)$p.value) #Was Beat NUll statis

@@

#MSOA Model
```{r}

    #as.formula(Reference ~ AffordRank+ AffordRank2+ TourismDensityRank)

set.seed(1983)
TestResample <- 1:100 %>% map(~  resample_partition(MSOAMean , c(test = 0.2, train = 0.8)))

#Make a lot of models

Combos <- expand.grid(1:2,1:3)

MSOAModels <- map2_df(.x = c("HighVal", "HighLUP")[Combos[,1]], .y = c(as.formula(Reference ~ HomesMedian+ AffordRank), 
                                                         as.formula(Reference ~ TourismDensityRank+ AffordRank),
                                                         as.formula(Reference ~ TourismDensityRank+ AffordRank+ AffordRank2))[Combos[,2]],
        ~{
          print(paste(.x,.y))
          MSOAMean %>% #LADMean %>%
    rename_(Reference = .x ) %>%
  ResampledModelPerf(., TestResample,  .y) %>%
            mutate(Dependent = .x,
                   Formula = toString(.y))

        } ) %>%
  mutate(type = ifelse(grepl("2", Formula), "2", "1"),
          Formula = ifelse(grepl("Tourism", Formula), "Tourism", "Price")
         )

MODOut <- 1:length(TestResample) %>% map_df(~{
  Mod2 <- LADMean  %>%
    rename(Reference = HighVal) %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$train)) %>%
  glm(formula = as.formula(Reference ~ TourismDensityRank+ AffordRank), data = ., family=binomial(link='logit')) %>%
    tidy

})

ggplot(MODOut, aes(x = term, y = estimate)) + geom_boxplot()

MSOAModelSumm <- MSOAModels %>%
  group_by(Dependent, Formula, type) %>%
  summarise(BeatNull = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            meanAcc = mean(Accuracy), #What was the mean accuracy
            NULLmod = mean(AccuracyNull),
            DiffNull = mean(Accuracy-AccuracyNull), #Mean difference relative to NULL
            StatistSignif = t.test(Accuracy,AccuracyNull, alternative = "greater", paired = T)$p.value) #Was Beat NUll statis

@@

>>>>

---
title: "Untitled"
author: "Jonathan Bourne"
date: "9 August 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---
Mang en natt har jeg sittet opp og skrevet dype romaner paa dette skrivebordet. Det er pent brukt, men har gitt meg graa haar. Det er som min Moby Dick, jeg har aldri helt klart aa temme det, boken er halvskrevet, hodet fult, hjertet tomt. Derfor maa det bort, kona orker ikke at jeg sitter oppe og stirrer paa uskrevne linjer i min moleskinen mer.

@@

Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up 2/Figures" #file.path(basewd, "Figures")
TexTables <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up 2/Tables"
suppressMessages(source(file.path(CommonCode, "AuxdataLoad.R")))
```

@@

This chunk processes all the areas and combines into a single dataframe
It also cleans all postcodes that are in other LADs out... should it just combine them into the other LADs LSOA?
```{r}
#creates a data frame called DATAdf
suppressMessages(source(file.path(SubCode, "LOADandProcessLADData.R")))

rm(PstCdLSOA.raw)
```

@@

rm(DataCover)

#Calculate Quantiles

This rather long winded way of getting the quartiles is important as it weights the sampling by Homes in an area. Relative proportion of sales in an area is not the same as homes. Some areas have higher turnover other lower. This means the quartiles need to be repeatedly sampled to get the right quartiles for the whole dataset.

In the below chunk I have sampled the data 501 times, however it is only necessary to sample one the quartiles don't change.

#Create a data frame of LSO
PriceCounts <-prices %>%
  filter(X5 %in% c("D", "S", "T", "F")) %>%
  group_by(LSOA11CD) %>%
  summarise(counts = n()) %>%
  arrange(counts)
##The subsampling is 1/10 of the number of homes in each LSOA, this stops crashes
PriceCounts<- EW2 %>%
  select(LSOA11CD = ECODE, Homes, Pop, LAD11CD, MSOA11CD) %>%
  left_join(.,PriceCounts, by = "LSOA11CD") %>%
  mutate(counts = ifelse(is.na(counts), 0, counts),
         Homes2 = Homes/10) %>%
  filter(counts!=0)

#Create a list of price vectors by LSOA
#This process can take a while
setwd(basewd)
if(file.exists("LSOAPriceList2.rds")){

  LSOAPriceList <- readRDS("LSOAPriceList2.rds")

}else{

  LSOAPriceList <- 1:nrow(PriceCounts) %>% map(~{
   print(.x)
    prices %>%
      filter(LSOA11CD==PriceCounts$LSOA11CD[.x], 
             X5 %in% c("D", "S", "T", "F")) %>%
      pull(X2)
    })
  names(LSOAPriceList) <- PriceCounts$LSOA11CD
  saveRDS(LSOAPriceList, "LSOAPriceList2.rds")

}

if(file.exists("AllDataQuartiles.rds")){

  AllDataQuartiles <- readRDS("AllDataQuartiles.rds")

}else{
  #Subset list to only the LADs used in analyis
  LSOAPriceList2 <- LSOAPriceList[names(LSOAPriceList) %in% unique(DATAdf$LSOA11CD)]
  PriceCounts2 <- PriceCounts %>%
    filter(LSOA11CD %in% unique(DATAdf$LSOA11CD))

  AllDataQuartiles <- StratifiedBoot(LSOAPriceList2, 
                                     PriceCounts2$LSOA11CD, 
                                     PriceCounts2$Homes2, 
                                     samples = 501) #change to 1 for a quicker solution has no effect on outcome

  saveRDS(AllDataQuartiles, "AllDataQuartiles.rds")

  rm(list = c("LSOAPriceList2", "PriceCounts2"))

}

AllDataQuartilesSummary <- AllDataQuartiles %>%
  summarise_all(funs(mean, sd))

BasicQuartiles <- prices$X2 %>% .[prices$LAD11CD %in% unique(DATAdf$LAD11CD)] %>% quantile(.)

#difference between the two up to 8% this has knock on effects later in the analysis if the quartiles are not calculated correctly
AllDataQuartilesSummary[2:4]/BasicQuartiles[2:4]

#Add the balanced quartiles on to the prices.
prices <- prices %>%
  mutate(CountryClass = cut(X2, AllDataQuartilesSummary[2:4] %>% c(0,., Inf), 
                              labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
                              right = F) %>% fct_relevel(., "Upper", after = 3))

rm(BasicQuartiles);rm(AllDataQuartiles);rm(AllDataQuartilesSummary);rm(LSOAPriceList)

@@

Needed for creating the skew plots
```{r}
setwd(file.path(basewd, "BootstrapQuartiles"))
BootstrapAllData(DATAdf, LimitValue = 1.4e5, Reps = 501)
BootStrapQuartiles <- LoadBootstrapData()

@@

##MSOA Bootstrap
Used for most of the analysis
```{r}
setwd(file.path(basewd, "BootstrapMSOA"))
BootstrapAllData(DATAdf, LimitValue = 1.4e5, Reps = 501, GroupingVars = "MSOA11CD")
BootStrapMSOA <- LoadBootstrapData()

@@

```{r}
CleanForPlotClassDiff <- function(df){ #not a seperate function for ease of editing
  df %>%  
  group_by(ID, Class) %>%
  summarise(Homes = sum(Homes), 
            LowUse = sum(LowUse)) %>%
  group_by(ID)%>%
  mutate(LowUseDistrib = LowUse/sum(LowUse),
         HomesDistrib = Homes/sum(Homes)) %>%
  mutate(LowUseRatio1 = (LowUseDistrib/0.25)-1,
         HomesRatio1 = (HomesDistrib/0.25)-1,
         LowUseRatio2 = (LowUseDistrib-HomesDistrib)/HomesDistrib) %>%
    ungroup
}

LADS<-DATAdf%>%
  group_by(LAD11CD) %>%
  summarise(LAD11NM = first(LAD11NM)) %>%
  arrange(LAD11NM)

#Plot for all data
All_data_class <- BootStrapQuartiles %>% 
  bind_rows %>%
  select(CountryClass, ID, LowUse, Homes) %>%
  rename(Class = CountryClass)

BootStrapQuartiles$E09000020  %>% CleanForPlotClassDiff()  %>%PlotClassDiff(Var = "HomesRatio1")
BootStrapQuartiles$E08000032 %>% CleanForPlotClassDiff()  %>%PlotClassDiff(Var = "HomesRatio1")
All_data_class %>% CleanForPlotClassDiff()  %>%PlotClassDiff(Var = "LowUseRatio2")

#All data summary
All_data_class %>% 
  group_by(Class,ID) %>%
  summarise_all(sum) %>%
  group_by(Class) %>%
  summarise_all(mean) %>%
  CleanForPlotClassDiff()

#Create multi panel plot for two areas and all data
bind_rows(
CleanForPlotClassDiff(BootStrapQuartiles$E09000020) %>% mutate(Area = "Kensington and Chelsea"),
CleanForPlotClassDiff(BootStrapQuartiles$E08000032) %>% mutate(Area = "Bradford"),
CleanForPlotClassDiff(All_data_class) %>% mutate(Area = "All Data")
) %>%
  mutate(Area = factor(Area, levels = c("Bradford", "All Data", "Kensington and Chelsea"))) %>%
  PlotClassDiff(Var = "LowUseRatio1") +
    facet_wrap(.~Area) +
  ggtitle("Difference in Low-Use Property distribution by Price Quartile")
SaveFig("ClassdiffAllData.pdf")

rm(BootStrapQuartiles);rm(All_data_class)
```

@@

```{r}
setwd(file.path(basewd, "VOA data"))

@@

```{r}
LADModelData <-CreateGeogModelData("LAD", file.path(basewd, "BootstrapMSOA"))
LADMean <- MeanModelData(LADModelData, "LAD") %>%
  mutate(AffordRank2 = scale(AffordRank)^2,
           AffordRatio2 = scale(AffordRatio)^2,
         TourismDensityRank = rank(TourismDensity, ties.method = "max"),
         LowUseType =case_when(
    "TRUE"==HighLUP & "TRUE" ==HighVal ~ 1, # All high
    "TRUE" == HighLUP & "FALSE" ==HighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==HighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==HighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  LowUseAfford =case_when(
    "TRUE"==HighLUP & AffordRank>=0.5 ~ 1, # All high
    "TRUE" == HighLUP & AffordRank<0.5 ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & AffordRank>=0.5 ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & AffordRank<0.5 ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor)  %>%
  left_join(MSOAtoLAD %>%
              group_by(LAD11CD) %>%
              summarise(LAD11NM = first(LAD11NM)), by = "LAD11CD")

  LADMean %>%
  ggplot(aes(x= AffordRank, y = LowUseRank, colour = LowUseAfford)) + geom_point() +
    geom_vline(xintercept  = 0.5)+
    geom_hline(yintercept = 0.5) +
    labs(title = "Seperating Low-Use type  by affordability", x = "Affordability percentage rank", y = "Low-Use percentile rank")
  SaveFig("LowUseAffordcolour.pdf")

@@

```{r}
MSOAModelData <-CreateGeogModelData("MSOA", file.path(basewd, "BootstrapMSOA")) 
MSOAMean <- MeanModelData(MSOAModelData, "MSOA") %>%
  left_join(select(MSOAtoLAD, MSOA11CD, LAD11CD)) %>%
  mutate(AffordRank2 = scale(AffordRank)^2,
         AffordRatio2 = scale(AffordRatio)^2,
         TourismDensityRank = rank(TourismDensity, ties.method = "max")) %>%
  left_join(select(LADMean, LAD11CD, LADHighLUP = HighLUP, LADHighVal = HighVal, #Add in Saucy LAD variables
                   LADAffordRatio = AffordRatio, LADAffordRatio2 = AffordRatio2,
                   LADTourismDensity = TourismDensity, LADMedianDiff = MedianDiff), by = "LAD11CD") %>%
  mutate(BothHighLUP =case_when(
    "TRUE"==HighLUP & "TRUE" ==LADHighLUP ~ 1, # all high
    "TRUE" == HighLUP & "FALSE" ==LADHighLUP ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==LADHighLUP ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==LADHighLUP ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  BothHighVal =case_when(
    "TRUE" ==HighVal & "TRUE" ==LADHighVal ~ 1, # all high
   "TRUE" == HighVal & "FALSE"==LADHighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighVal & "TRUE" ==LADHighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighVal & "FALSE"==LADHighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor,
  MSOALUPLADVal =case_when(
    "TRUE" ==HighLUP & "TRUE" ==LADHighVal ~ 1, # all high
   "TRUE" == HighLUP & "FALSE"==LADHighVal ~ 2, #High LUP in MSOA but not in LAD
    "FALSE"==HighLUP & "TRUE" ==LADHighVal ~ 3, #High LUP in LAD but not MSOA
    "FALSE"==HighLUP & "FALSE"==LADHighVal ~ 4 #LOW LUP in both LAD and MSOA
  ) %>% as.factor
           )

 MSOAMean %>%
   #filter(TourismDensity!= 0) %>%
  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighLUP)) + geom_point()

  MSOAMean %>%
   #filter(TourismDensity!= 0) %>%
  ggplot(aes(x= AffordRank, y = TourismDensity, colour = BothHighLUP)) + geom_point()

   MSOAMean %>%
   filter(TourismDensity!= 0) %>%
  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighVal)) + geom_point()

      MSOAMean %>%
   filter(TourismDensity!= 0) %>%
  ggplot(aes(x= AffordRank, y = TourismDensity, colour = BothHighVal)) + geom_point()

  MSOAMean %>%
  ggplot(aes(x= MedianDiffRank, y = LowUseRank, colour = BothHighVal)) + geom_point()

@@

Plots that help explain the data seperation
```{r}
bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD")) %>%
  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighLUP)) + geom_point() +
  facet_wrap(~type) + 
  labs(title = "Does the geography have above the median LUPs", x = "Affordability Rank", y = "Tourism Density") +
  guides(fill=guide_legend(title="Above Median"))
SaveFig("HighLUP.pdf")

bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD")) %>%
  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighVal)) + geom_point() +
  facet_wrap(~type) + 
  labs(title = "Is the median LUP price higher than the Median price of all properties", x = "Affordability Rank", y = "Tourism Density") +
  guides(fill=guide_legend(title="Above Median"))
SaveFig("HighVal.pdf")

@@

#Model Combinations

The below are the combinations of formula and outcome variable

Outcomes <- c("HighVal", "HighLUP")
OutcomesLinear <- c("LowUsePerc", "MedianDiff")

Formulas <- c(as.formula(Reference ~ AffordRatio),
   as.formula(Reference ~ TourismDensity + AffordRatio),
      as.formula(Reference ~ AffordRatio + AffordRatio2),
   as.formula(Reference ~ TourismDensity + AffordRatio + AffordRatio2))

@@

@@

cv <- tidy(vfold_cv(mtcars, v = 5))

cv <- tidy(vfold_cv(mtcars, v = 5, repeats = 2))

#Create sample
set.seed(1983)
TestResample <- 1:100 %>% map(~  resample_partition(LADMean , c(test = 0.2, train = 0.8)))

#Create a load of classifiers
LADModels <- LinearClassifierCombiner(LADMean,  Outcomes, Formulas, TestResample) %>%
  mutate(IncAfford2 = grepl("2", Formula),
           IncTourism = grepl("Tourism", Formula)
         )

#Create a load of linear models
LADModelsLin <- LinearClassifierCombiner(LADMean,  OutcomesLinear, Formulas, TestResample, Classifier = FALSE) %>%
  mutate(IncAfford2 = grepl("2", Formula),
           IncTourism = grepl("Tourism", Formula)
         )

LADModels %>%
  group_by(Dependent, IncAfford2, IncTourism) %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            ) %>%
  ungroup %>%
   mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  rename(Afford2 = IncAfford2,
         Tourism = IncTourism) %>% mutate(ModelID = rep(1:4,2))

#Linear models are rubbish
LADModelsLin %>%
  select(-sample) %>%
  group_by(Dependent, IncAfford2, IncTourism) %>%
  summarise_if(is.numeric, funs(mean))

#Explore the best classifier
#There is no structure which adequately models whether A LAD will have more than the median LUP percentage
LADMODOut2 <- ExtractClassCoeffs(LADMean, "HighLUP", TestResample, Formulas[[1]])
LADMODOut2 %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
LADMODOut2 %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have hhigh value LUPs
LADMODOut <- ExtractClassCoeffs(LADMean, "HighVal", TestResample, Formulas[[2]])
LADMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
LADMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

LADMODOut %>%
  select(-statistic, -std.error) %>%
  group_by(term) %>%
  summarise_all(funs(mean, median))

@@

#MSOA Model
```{r}
set.seed(1983)
TestResample <- 1:100 %>% map(~  resample_partition(MSOAMean , c(test = 0.2, train = 0.8)))

MSOAModels <-LinearClassifierCombiner(MSOAMean,  Outcomes, Formulas, TestResample) %>%
  mutate(IncAfford2 = grepl("2", Formula),
           IncTourism = grepl("Tourism", Formula)
         )

MSOAModelsLin <- LinearClassifierCombiner(MSOAMean,  OutcomesLinear, Formulas, TestResample, Classifier = FALSE) %>%
  mutate(IncAfford2 = grepl("2", Formula),
           IncTourism = grepl("Tourism", Formula)
         )

MSOAModels %>%
  group_by(Dependent, IncAfford2, IncTourism) %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            ) %>%
  ungroup %>%
   mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
  rename(Afford2 = IncAfford2,
         Tourism = IncTourism)

#Including both tourism and the quadratic affordability term produces the best model. Which makes sense given the plot earlier
LADMODOut <- ExtractClassCoeffs(MSOAMean, "HighLUP", TestResample, Formulas[[4]])
LADMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
LADMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have hhigh value LUPs
MSOAMODOut2 <- ExtractClassCoeffs(MSOAMean, "HighVal", TestResample, Formulas[[1]])
MSOAMODOut2 %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
MSOAMODOut2 %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values

MSOAMODOut %>%
  select(-statistic, -std.error) %>%
  group_by(term) %>%
  summarise_all(funs(mean, median))

#Rubbish
MSOAModelsLin %>%
  select(-sample) %>%
  group_by(Dependent, IncAfford2, IncTourism) %>%
  summarise_if(is.numeric, mean, na.rm = T)

@@

Take away message is that the LAD model cannot predict LUP% whilst the MSOA model cannot predict High LUP Value
